---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# nghiaagentrutils

<!-- badges: start -->
<!-- badges: end -->

I set up this packages to centralise some frequently used functions:  

- `recode_msigdbh`: Make MSigDB Hallmark gene set names more readable.

## Installation

You can install the development version of nghiaagentrutils from [GitHub](https://github.com/) with:

```{r, message = FALSE, warning = FALSE}
# install.packages("pak")
pak::pak("nghiaagent/nghiaagentrutils")
```

## Examples

### Making MSigDB Hallmark gene set names more readable

Simply supply the `recode_msigdbh()` function with your vector of MSigDB Hallmark gene set names!

Ideally, the gene set names are derived from the publicly available GMT files at [https://www.gsea-msigdb.org/gsea/msigdb](https://www.gsea-msigdb.org/gsea/msigdb)

```{r, include = FALSE}
renv::restore()
library(nghiaagentrutils)
```

```{r example}
## Example
x <- c(
  "HALLMARK_ADIPOGENESIS",
  "HALLMARK_G2M_CHECKPOINT",
  "HALLMARK_IL6_JAK_STAT3_SIGNALING"
)
recode_msigdbh(x)
```
